Data for the Ontario Restaurant Closures Experiment

### 2021-02-18 outputs/paper/data_simulation.Rmd
data simulation done, all in-text references in data_simulation, first test knits run on both paper and data_simulation

 service_percentage
```
According to Ontario restaurant data from Yelp (cite, KSondjaja source), approximately 6% of restaurants
offer dine in service, 32.5% offer takeout, and 61.5% offer both.

## Survey 1
```{r}
set.seed(19)
survey_1 <- survey_1 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))
```

## Survey 2
```{r}
set.seed(19)
survey_2 <- survey_2 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))
```

@@

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))
```

## Survey 2
```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))
```

Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
GEO_CODE indicates public health regions, taken from Census 2016 links:
https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
```{r}
### Load census dataset by Health Regions ###
census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
census_2016 <- janitor::clean_names(census_2016)

### Select demographic data to include, relating to employment, income, immigration status, minority groups, commute, etc. ###
# Many categories
# demographic_info <- c(1, 6, 8:33, 60:67, 100:104, 661:663, 694:707, 724:726, 1135:1136, 1139, 1140:1150, 1157, 1158, 1170, 1188, 1198, 1216, 1287, 1289:1292, 1324:1337, 1683:1697, 1884:1929)

@@

### Get data from the randomly selected Health Regions ###

@@

populations_split_percentage
```
https://www150.statcan.gc.ca/n1/pub/89-656-x/89-656-x2015001-eng.htm
Indigenous groups are 4% of the population.

https://www.statcan.gc.ca/eng/dai/btd/othervisuals/other010
visible minorities are 25% of the population

https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
1.4% of business owners are indigenous, and 12.2% are visible minorities.

Therefore, Indigenous people are 0.35 times as likely to own a business, and visible minorities are 0.49 as likely to own a business.

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

@@

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

@@

@@

From an analysis of Kaggle restaurant data [@kagglerestaurantdata], we can see that restaurant revenue looks like an F distribution.
The distribution rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) gives an approximate shape. Using the f-distribution formula, we know the distribution has a mean of 5/3, so we would multiply by 41,975 to get the mean to 69,959.

```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(revenue = 41975 * rf(num_total,10,5))
```

@@

There seems to be no significant difference in business losses for disabled owners [@aug20192020].

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(revenue = 41975 * rf(num_total,10,5)) %>%
  mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
  mutate(revenue = factor * revenue) %>%
  select(-factor)

@@

<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<CHECK IF THIS WORKS ONCE MINORITY DATA IS ADDED AMY>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
survey_2 <-
  bind_rows(
    survey_2 %>%
      filter((minority == "yes" | indigenous == "yes") & group == "treatment") %>%
      mutate(revenue = 0.88 * revenue)
    ,
    survey_2 %>%
      filter(minority == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

# Number of employees
LALA
## Survey 1
```{r}
survey_1 <- survey_1 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

## Survey 2
```{r}
survey_2 <- survey_2 %>%
  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
```

@@

```{r}
num_cols_1 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>

@@

```{r}
num_cols_2 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>

@@

survey_2 <- survey_2 %>%
  select(-nonresponse, -which_partial)
```

>>>>

 service_percentage
```
According to Ontario restaurant data from Yelp [@yelp_dataset], approximately 6% of restaurants
offer dine in service, 32.5% offer takeout, and 61.5% offer both.

## Survey 1
```{r}
set.seed(19)
survey_1 <- survey_1 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

## Survey 2
```{r}
set.seed(19)
survey_2 <- survey_2 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

survey_2
```

@@

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

## Survey 2
```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no"),
                             size = num_total,
                             prob = c(0.005, .995),
                             replace = TRUE))

survey_2
```

```{r}
### Load census dataset by Health Regions ###
### Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
census_2016 <- janitor::clean_names(census_2016)

@@

### Get data from the randomly selected Health Regions ###
# GEO_CODE indicates public health regions, taken from Census 2016 links:
#https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0

@@

populations_split_percentage
```

We established expected percentages for the treatment and control regions based on census data [@census_2016].

15.6% of business owners are women in Canada [@ownershipdemos].

Visible minorities are 25% of the population [@visibleminority].

12.2% of business owners are visible minorities [@ownershipdemos].

Therefore, visible minorities are 0.49 as likely to own a business.
Therefore, we can estimate that 0.058 of restaurant owners are a visible minority in the treatment group, and 0.081 in the control group.

Indigenous people have 3.7% service business ownership as opposed to 15.3% in the reference population [@businessesper]. They are 0.24 times as likely to own a service business in Ontario.
Therefore, we can estimate that 0.009 of business owners in the treatment group are Indigenous, and 0.011 in the control group.

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))

set.seed(19893)
survey_1 <- bind_rows(
  survey_1 %>%
    filter(group == "treatment") %>%
    mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_treat, prob = c(0.009, 0.981, 0.01), replace = TRUE))
  ,
  survey_1 %>%
    filter(group == "control") %>%
   mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_control, prob = c(0.011, 0.979, 0.01), replace = TRUE))
)

set.seed(19893)
survey_1 <- bind_rows(
  survey_1 %>%
    filter(group == "treatment", indigenous != "yes") %>%
    mutate(visible = sample(c("yes", "no", "nonanswer"), 
                               size = first(count(survey_1 %>% filter(group == "treatment", indigenous != "yes"))), 
                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
  ,
  survey_1 %>%
    filter(group == "control", indigenous != "yes") %>%
   mutate(visible = sample(c("yes", "no", "nonanswer"), 
                              size = first(count(survey_1 %>% filter(group == "control", indigenous != "yes"))), 
                              prob = c(0.08, 0.91, 0.01), replace = TRUE))
  ,
  survey_1 %>%
    filter(indigenous == "yes") %>%
    mutate(visible = "no")
)

@@

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))

set.seed(19893)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment") %>%
    mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_treat, prob = c(0.009, 0.981, 0.01), replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control") %>%
   mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_control, prob = c(0.011, 0.979, 0.01), replace = TRUE))
)

set.seed(19893)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment", indigenous != "yes") %>%
    mutate(visible = sample(c("yes", "no", "nonanswer"), 
                               size = first(count(survey_2 %>% filter(group == "treatment", indigenous != "yes"))), 
                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control", indigenous != "yes") %>%
   mutate(visible = sample(c("yes", "no", "nonanswer"), 
                              size = first(count(survey_2 %>% filter(group == "control", indigenous != "yes"))), 
                              prob = c(0.08, 0.91, 0.01), replace = TRUE))
  ,
  survey_1 %>%
    filter(indigenous == "yes") %>%
    mutate(visible = "no")
)

survey_2
```

@@

survey_2
```

@@

From an analysis of Kaggle restaurant data [@kagglerestaurantdata], we can see that restaurant revenue looks like an F distribution.
The distribution rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) gives an approximate shape. Using the f-distribution formula, we know the distribution has a mean of 10/9, so we would multiply by 62,963 to get the mean to 69,959.

```{r}
set.seed(19894)
survey_1 <- survey_1 %>%
  mutate(revenue = 62963 * rf(num_total,20,20))

@@

There seems to be no significant difference in business losses for disabled owners or female business owners [@aug20192020].

```{r}
set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(revenue = 62963 * rf(num_total,20,20)) %>%
  mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
  mutate(revenue = factor * revenue) %>%
  select(-factor)

@@

survey_2 <-
  bind_rows(
    survey_2 %>%
      filter((visible == "yes" | indigenous == "yes") & group == "treatment") %>%
      mutate(revenue = 0.88 * revenue)
    ,
    survey_2 %>%
      filter(visible == "no" & group == "treatment")
    ,
    survey_2 %>%
      filter(group == "control")
  )

survey_2
```

# Number of employees

$82,000 in yearly sales (gross revenue) per full-time equivalent employee [@restfact]

Therefore 6,833 monthly revenue per full-time equivalent employee.

In January 2021, there were 2187300 full time sales and service employees in Canada and 1164000 part time sales and service employees [@hourswages].
Therefore there are 1.9 full time employees per part time employee.
Part time employees in service and sales averaged 16.6 hours per week. We will assume that 2 PTE = 1 FTE, or 1 PTE = 0.5 FTE.
Therefore, for every 1.9 + 1 employees, there are 1.9 + 1*0.5 FTE. For every 2.9 employees, there are 2.4 FTE.

2.4 FTE -> 1.9 FT + 1 PT.
0.79 = 1.9 / 2.4 = 1.9 / (1.9 + 0.5)
0.42 = 1 / 2.4 = 0.42 = 1 / (1.9 + 0.5)

## Survey 1
```{r}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ft = round(fte * 0.79)) %>%
  mutate(pt = round(fte * 0.42)) %>%
  select(-fte)

survey_1 <- bind_rows(
  survey_1 %>% filter(ft < 1) %>%
    mutate(ft = 1),
  survey_1 %>% filter(ft >= 1)
)

For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9. X is some number less than or equal to 1.9.
x / (x + 0.5)
1 / (x + 0.5)

```{r}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ptincrease = 1.9 * (1 - abs(rnorm(num_total, 0, sd = 0.1)))) %>%
  mutate(ft = round(fte * (ptincrease / (ptincrease + 0.5)))) %>%
  mutate(pt = round(fte * (1 / (ptincrease + 0.5)))) %>%
  select(-fte, - ptincrease)

survey_2 <- bind_rows(
  survey_2 %>% filter(ft < 1) %>%
    mutate(ft = 1),
  survey_2 %>% filter(ft >= 1)
)

survey_2
```

@@

```{r}
num_cols_1 = 11

@@

```{r}
num_cols_2 = 12

@@

survey_2 <- survey_2 %>%
  select(-nonresponse, -which_partial)

survey_2
```

```{r}
write_csv(survey_1, here("outputs/data/survey_1.csv"))
write_csv(survey_2, here("outputs/data/survey_2.csv"))
```
